---
title: "6th Tidy Tuesday"
author: "Ruth Vergara Reyes"
date: "4/1/2021"
output:
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE)
```

# Introduction

This is the 6th tidy tuesday I make

# Load Libraries
```{r}
library(tidyverse)
library(here)
library(RColorBrewer)
library(tidytuesdayR)
library(patchwork)
```


# Load Data
```{r, message=FALSE}

tues_data <- tidytuesdayR::tt_load(2021, week = 14)
ulta <- tues_data$ulta
sephora <- tues_data$sephora
allShades <- tues_data$allShades
allNumbers <- tues_data$allNumbers
allCategories <- tues_data$allCategories

```


# Data Analysis 

I will be looking at the color range of foundation available in Sephora and Ulta. I will be comparing ranges avalible at the different places and then one brand they have that is supposed to have wider ranges. 

### Cleaning up the data 
```{r}
top_brands_sephora <- c("Anastasia Beverly Hills", "bareMinerals", "Lancôme", "FENTY BEAUTY by Rihanna")  ### Three brands that are the same as Ulta and one that is supposed to have a wider range. #

top_brands_ulta <- c("Anastasia Beverly Hills","bareMinerals","Lancôme", "Maybelline")                    ### Three brands that are the same as Sephora and one that is supposed to have a wider range. #

clean_sephora <- sephora %>%
  filter (brand %in% top_brands_sephora) %>%            ### How I got the brands I wanted
  arrange(brand) %>%                                    ### How I got the brands to be in alphabetical order
  select(-url, -imgSrc, -imgAlt, -name)                 ### How I got rid of columns that I did not need

clean_ulta <- ulta %>%
  filter(brand %in% top_brands_ulta) %>%                ### How I got the brands I wanted to look at 
  select(-url, -imgSrc, -imgAlt,-name)%>%               ### How I got rid of columns that I did not need
  arrange(brand)                                        ### How I got the brands to get into alphabetical order

clean_seph_num <- allNumbers %>%                        ### This is how I cleaned the numbers data so I can join with precious data
  filter(brand %in% top_brands_sephora)%>%              ### How I got the information that I needed from the numbers data
  select(-name, -hex)                                   ### How I got rid of columns that I do not need

Seph_data <- inner_join(clean_seph_num, clean_sephora)  ### How I joined the two sets of data for Sephora into one big data set

clean_ulta_num <- allNumbers %>%                        ### This is the data set I will be joining with the previous ULta data set
  filter(brand %in% top_brands_ulta)%>%                 ### How I cleaned up the numbers data for the ulta brands
  select(-name, -hex)                                   ### How I got rid of columns that I do not need

ulta_data <- inner_join(clean_ulta_num, clean_ulta)     ### How I joined the two data sets for Ulta into one 

```

### Making the Plots
I will first  make two plots then combine them into one.

```{r}
##### Sephora Plot #####

seph_plot <- Seph_data %>%
  ggplot(aes(x = numbers,             
             y = lightness,
             color = lightness))+               ### What I chose for my x/y axis
  geom_point()+                                 ### Type of plot I used
  facet_wrap(~brand, scales = "free")+          ### How I got each brand to have its own small plot
  theme_classic()+                              ### Theme 
  labs(x = "Foundation Number",
       y = "Shade Range ",
       title = "Foundation Range by Popular Brands",
       subtitle = "This plot shows the shade ranges 
of foundation avaliable at Sephora based on the brand.")+ ### new labels for the plot ##
  theme(legend.box = "none",
        axis.title = element_text(size = 10),
        title = element_text(size = 16),
        plot.subtitle = element_text(size = 11),
        legend.position = "none")+              ### How I changed certain aspects of the plot
 ggsave(here("tidy_tuesday_6", "output", "seph_plot.png"),
       width = 10, height = 7)
seph_plot

##### Ulta Plot #####

ulta_plot <- ulta_data %>%
  ggplot(aes(x = numbers,             
             y = lightness,
             color = lightness))+               ### What I chose for my x/y axis
  geom_point()+                                 ### Type of plot I used
  facet_wrap(~brand, scales = "free")+          ### How I got each brand to have its own small plot
  theme_classic()+                              ### Theme 
  labs(x = "Foundation Number",
       y = "Shade Range",
       subtitle = "This plot shows the shade ranges of foundation 
avaliable at Ulta based on the brand.")+        ### new labels for the plot ##
  theme(legend.box = "none",
        axis.title = element_text(size = 10),
        title = element_text(size = 16),
        plot.subtitle = element_text(size = 11),
        legend.position = "none")+             ### How I changed certain aspects of the plot
  ggsave(here("tidy_tuesday_6", "output", "ulta_plot.png"),
       width = 10, height = 7)

ulta_plot
```


### Putting the plots together 
```{r}
seph_plot+ulta_plot +
  plot_layout(guides = 'collect')+
ggsave(here("tidy_tuesday_6", "output", "seph_ulta_plot.png"),
       width = 10, height = 7)
```


